Credit Risk Distribution and Capital Savings

### 2020-04-02 Analysis/Draft/Draft_bookdown.Rmd
Add code that allow control of column width in stargazer command

source("../../Auxiliar/Function.R") ## Capital requirements functions
source("../../Auxiliar/longtable.R") ## longtable for stargazer

@@

```{r summary_control, fig.height = 10, fig.width = 7, results="asis",out.width = "1\\textwidth"}
bank.data.win %>% select(
  log.gdp_gr,
  log.gdp,
  credit_gdp,
  pillarI_stringency,
  cap_reg,
  Sup_Power,
  log.asset,
  NPL.ratio,
  Zscore,
  ROE,
  ROA) %>%
  as.data.frame() %>% 
stargazer(header = FALSE, type="latex", single.row = TRUE, column.sep.width = "1pt", font.size = "footnotesize",
          label = "tab:summary",
          omit.summary.stat = c("p25","p75"),
          covariate.labels = 
            c("$\\Delta \\text{Log GDP}$",
              "Log GDP",
              "Credit / GDP",
              "Capital Stringency Index",
              "Pillar I Stringency",
              "Official Supervisory Power",
              "Log Total Assets",
              "Non-performing Loans / Loans",
              "Z-score",
              "ROE",
              "ROA"),
          notes.label = "",
          notes.align = "c", 
          notes.append = FALSE,
          summary = TRUE,
          digits = 3,
          float = FALSE)
```

>>>>

source("../../Auxiliar/Function.R") ## Capital requirements functions
source("../../Auxiliar/longtable.R") ## longtable for stargazer
source("../../Auxiliar/adj_stargazer.R") ## adjust the first column width for stargazer

@@

```{r summary_control, fig.height = 10, fig.width = 7, results="asis",out.width = "1\\textwidth"}
table <- capture.output({bank.data.win %>% ungroup()%>% select(
  log.gdp_gr,
  log.gdp,
  credit_gdp,
  pillarI_stringency,
  cap_reg,
  Sup_Power,
  log.asset,
  NPL.ratio,
  Zscore,
  ROE,
  ROA) %>%
  as.data.frame() %>% 
stargazer(header = FALSE, type="latex", single.row = TRUE, column.sep.width = "1pt", font.size = "footnotesize",
          label = "tab:summary",
          omit.summary.stat = c("p25","p75"),
          covariate.labels = 
            c("$\\Delta \\text{Log GDP}$",
              "Log GDP",
              "Credit / GDP",
              "Capital Stringency Index",
              "Pillar I Stringency",
              "Official Supervisory Power",
              "Log Total Assets",
              "Non-performing Loans / Loans",
              "Z-score",
              "ROE",
              "ROA"),
          notes.label = "",
          notes.align = "c", 
          notes.append = FALSE,
          summary = TRUE,
          digits = 3,
          float = FALSE)})

table <- gsub("lccccc",
              "p{0.4\\textwidth}ccccc", table, fixed = T)

cat(table)
```
